### 2023-03-06 README.Rmd
Add CRAN post-acceptance things [no CI]
Fix README about Woody Ref #67 [no ci]
Update doc regarding R 1.3.1 support [no ci]

@@

`rang` can still be used to recreate computational environments for R < 3.1.0. The Dockerfile generated is based on Debian Woody (3.0) and the requested version of R is compiled from source. As of writing, this method works for R < 3.1.0 but not R < 2.1.0. The `image` parameter is ignored in this case.

>>>>

Or the stable CRAN version

```r
install.packages("rang")
```

@@

`rang` can still be used to recreate computational environments for R < 3.1.0. The Dockerfile generated is based on Debian Lenny (5.0) and the requested version of R is compiled from source. As of writing, this method works for R < 3.1.0 but not R < 1.3.1. The `image` parameter is ignored in this case.
